---
title: "R Notebook"
output: html_notebook
---

```{r setup, include=FALSE, warning=F, error=F}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(car)
library(DescTools)
```

## Import Response Data
```{r}
rm(list = ls())
evals_dir = "../results/"
data1 = "main_constructs"
data2 = "additional_constructs"

# results_path = paste(evals_dir, paste(corp, "success", type, mode, sep="_"), ".csv", sep="") #bert
results_path = paste(evals_dir, paste(data1, ".csv", sep="") , sep="") #chatGPT
results_path2 = paste(evals_dir, paste(data2, ".csv", sep="") , sep="") #chatGPT - second set of constructs

df <- read.csv(results_path) # load predictions
df2 <- read.csv(results_path2) # load predictions set 2
df <- rbind(df, df2) # combine both
print(nrow(df %>% distinct(id, source, prompt_type, construct, item)) - nrow(df)) #check if queries are doubled

# print(nrow(df))
# n_constr = length(unique(df[, "construct"]))
```

## Get Performance
### CCR Data
```{r}
df_scores_behavior = read.csv("../data/behavior_survey.csv")
df_scores_behavior = cbind(source = "behaviors", df_scores_behavior)
df_scores_values = read.csv("../data/values_survey.csv")
df_scores_values = cbind(source = "values", df_scores_values)
df_scores_all = rbind(df_scores_behavior, df_scores_values)
names(df_scores_all)[names(df_scores_all) == 'X'] <- 'model'
```


### GPT item-level models (using responses from CCR style prompts) -- Values essays
```{r}
#reformat data sets from long to wide for each construct separately
#only use responses from CCR style prompt
df_ccr_cons = df %>% filter(construct=="conservatism_tot" & prompt_type=="hybrid" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_ccr_indi = df %>% filter(construct=="Individualism_tot" & prompt_type=="hybrid" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_ccr_reli = df %>% filter(construct=="Religiosity_tot" & prompt_type=="hybrid" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_ccr_coll = df %>% filter(construct=="Collectivism_tot" & prompt_type=="hybrid" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_ccr_care = df %>% filter(construct=="CARE_tot" & prompt_type=="hybrid" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_ccr_equa = df %>% filter(construct=="EQUALITY_tot" & prompt_type=="hybrid" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_ccr_prop = df %>% filter(construct=="PROPORTIONALITY_tot" & prompt_type=="hybrid" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_ccr_loya = df %>% filter(construct=="LOYALTY_tot" & prompt_type=="hybrid" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_ccr_auth = df %>% filter(construct=="AUTHORITY_tot" & prompt_type=="hybrid" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_ccr_puri = df %>% filter(construct=="PURITY_tot" & prompt_type=="hybrid" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_ccr_nfc = df %>% filter(construct=="NFC_tot" & prompt_type=="hybrid" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_ccr_tigh = df %>% filter(construct=="Tightness" & prompt_type=="hybrid" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_ccr_sd = df %>% filter(construct=="PVQ_SD_tot" & prompt_type=="hybrid" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_ccr_po = df %>% filter(construct=="PVQ_PO_tot" & prompt_type=="hybrid" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_ccr_un = df %>% filter(construct=="PVQ_UN_tot" & prompt_type=="hybrid" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_ccr_ac = df %>% filter(construct=="PVQ_AC_tot" & prompt_type=="hybrid" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_ccr_se = df %>% filter(construct=="PVQ_SE_tot" & prompt_type=="hybrid" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_ccr_st = df %>% filter(construct=="PVQ_ST_tot" & prompt_type=="hybrid" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_ccr_co = df %>% filter(construct=="PVQ_CO_tot" & prompt_type=="hybrid" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_ccr_tr = df %>% filter(construct=="PVQ_TR_tot" & prompt_type=="hybrid" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_ccr_he = df %>% filter(construct=="PVQ_HE_tot" & prompt_type=="hybrid" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_ccr_be = df %>% filter(construct=="PVQ_BE_tot" & prompt_type=="hybrid" & source=="values") %>% spread(key = "item", value = "prediction_clean")

gpt_ccr_cons_lm <- lm(response ~ item_1 + item_2, df_ccr_cons)
gpt_ccr_indi_lm <- lm(response ~ item_1 + item_2 + item_3 + item_4 + item_5 + item_6, df_ccr_indi)
gpt_ccr_reli_lm <- lm(response ~ item_1 + item_2 + item_3 + item_4 + item_5,          df_ccr_reli)
gpt_ccr_coll_lm <- lm(response ~ item_1 + item_2 + item_3 + item_4 + item_5 + item_6, df_ccr_coll)
gpt_ccr_care_lm <- lm(response ~ item_1 + item_2 + item_3 + item_4 + item_5 + item_6, df_ccr_care)
gpt_ccr_equa_lm <- lm(response ~ item_1 + item_2 + item_3 + item_4 + item_5 + item_6, df_ccr_equa)
gpt_ccr_prop_lm <- lm(response ~ item_1 + item_2 + item_3 + item_4 + item_5 + item_6, df_ccr_prop)
gpt_ccr_loya_lm <- lm(response ~ item_1 + item_2 + item_3 + item_4 + item_5 + item_6, df_ccr_loya)
gpt_ccr_auth_lm <- lm(response ~ item_1 + item_2 + item_3 + item_4 + item_5 + item_6, df_ccr_auth)
gpt_ccr_puri_lm <- lm(response ~ item_1 + item_2 + item_3 + item_4 + item_5 + item_6, df_ccr_puri)

gpt_ccr_nfc_lm <- lm(response ~ item_1 + item_2 + item_3 + item_4 + item_5 + item_6, df_ccr_nfc)
gpt_ccr_tigh_lm <- lm(response ~ item_1 + item_2 + item_3 + item_4 + item_5 + item_6, df_ccr_tigh)

gpt_ccr_sd_lm <- lm(response ~ item_1 + item_2, df_ccr_sd)
gpt_ccr_po_lm <- lm(response ~ item_1 + item_2, df_ccr_po)
gpt_ccr_un_lm <- lm(response ~ item_1 + item_2 + item_3, df_ccr_un)
gpt_ccr_ac_lm <- lm(response ~ item_1 + item_2, df_ccr_ac)
gpt_ccr_se_lm <- lm(response ~ item_1 + item_2, df_ccr_se)
gpt_ccr_st_lm <- lm(response ~ item_1 + item_2, df_ccr_st)
gpt_ccr_co_lm <- lm(response ~ item_1 + item_2, df_ccr_co)
gpt_ccr_tr_lm <- lm(response ~ item_1 + item_2, df_ccr_tr)
gpt_ccr_he_lm <- lm(response ~ item_1 + item_2, df_ccr_he)
gpt_ccr_be_lm <- lm(response ~ item_1 + item_2, df_ccr_be)
```


### GPT item-level scores (CCR style prompts) -- Values essays
```{r}
#model summaries
gpt_ccr_cons_summary = summary(gpt_ccr_cons_lm)
gpt_ccr_indi_summary = summary(gpt_ccr_indi_lm)
gpt_ccr_reli_summary = summary(gpt_ccr_reli_lm)
gpt_ccr_coll_summary = summary(gpt_ccr_coll_lm)
gpt_ccr_care_summary = summary(gpt_ccr_care_lm)
gpt_ccr_equa_summary = summary(gpt_ccr_equa_lm)
gpt_ccr_prop_summary = summary(gpt_ccr_prop_lm)
gpt_ccr_loya_summary = summary(gpt_ccr_loya_lm)
gpt_ccr_auth_summary = summary(gpt_ccr_auth_lm)
gpt_ccr_puri_summary = summary(gpt_ccr_puri_lm)

gpt_ccr_nfc_summary = summary(gpt_ccr_nfc_lm)
gpt_ccr_tigh_summary= summary(gpt_ccr_tigh_lm)
gpt_ccr_sd_summary= summary(gpt_ccr_sd_lm)
gpt_ccr_po_summary= summary(gpt_ccr_po_lm)
gpt_ccr_un_summary= summary(gpt_ccr_un_lm)
gpt_ccr_ac_summary= summary(gpt_ccr_ac_lm)
gpt_ccr_se_summary= summary(gpt_ccr_se_lm)
gpt_ccr_st_summary= summary(gpt_ccr_st_lm)
gpt_ccr_co_summary= summary(gpt_ccr_co_lm)
gpt_ccr_tr_summary= summary(gpt_ccr_tr_lm)
gpt_ccr_he_summary = summary(gpt_ccr_he_lm)
gpt_ccr_be_summary = summary(gpt_ccr_be_lm)

scores_gpt_ccr_values = c(gpt_ccr_tigh_summary$r.squared, gpt_ccr_indi_summary$r.squared,
                          gpt_ccr_coll_summary$r.squared, gpt_ccr_nfc_summary$r.squared,
                          gpt_ccr_cons_summary$r.squared, gpt_ccr_reli_summary$r.squared,
           gpt_ccr_care_summary$r.squared, gpt_ccr_equa_summary$r.squared,
           gpt_ccr_prop_summary$r.squared, gpt_ccr_loya_summary$r.squared,
           gpt_ccr_auth_summary$r.squared, gpt_ccr_puri_summary$r.squared,
           gpt_ccr_sd_summary$r.squared, gpt_ccr_po_summary$r.squared,
           gpt_ccr_un_summary$r.squared, gpt_ccr_ac_summary$r.squared,
           gpt_ccr_se_summary$r.squared, gpt_ccr_st_summary$r.squared,
           gpt_ccr_co_summary$r.squared, gpt_ccr_tr_summary$r.squared,
            gpt_ccr_he_summary$r.squared, gpt_ccr_be_summary$r.squared)

names(scores_gpt_ccr_values) <- colnames(df_scores_all)[3:length(colnames(df_scores_all))]

df_scores_gpt_ccr_values <- as.data.frame(t(data.frame(scores_gpt_ccr_values)))
df_scores_gpt_ccr_values = cbind(source = "values", df_scores_gpt_ccr_values)
df_scores_gpt_ccr_values = cbind(model = "gpt_ccr", df_scores_gpt_ccr_values)
```


### GPT item-level models (CCR style prompts) -- Everyday essays
```{r}
#reformat data sets from long to wide for each construct separately
#only use responses from CCR style prompt
df_ccr_cons = df %>% filter(construct=="conservatism_tot" & prompt_type=="hybrid" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_ccr_indi = df %>% filter(construct=="Individualism_tot" & prompt_type=="hybrid" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_ccr_reli = df %>% filter(construct=="Religiosity_tot" & prompt_type=="hybrid" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_ccr_coll = df %>% filter(construct=="Collectivism_tot" & prompt_type=="hybrid" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_ccr_care = df %>% filter(construct=="CARE_tot" & prompt_type=="hybrid" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_ccr_equa = df %>% filter(construct=="EQUALITY_tot" & prompt_type=="hybrid" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_ccr_prop = df %>% filter(construct=="PROPORTIONALITY_tot" & prompt_type=="hybrid" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_ccr_loya = df %>% filter(construct=="LOYALTY_tot" & prompt_type=="hybrid" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_ccr_auth = df %>% filter(construct=="AUTHORITY_tot" & prompt_type=="hybrid" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_ccr_puri = df %>% filter(construct=="PURITY_tot" & prompt_type=="hybrid" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_ccr_nfc = df %>% filter(construct=="NFC_tot" & prompt_type=="hybrid" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_ccr_tigh = df %>% filter(construct=="Tightness" & prompt_type=="hybrid" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_ccr_sd = df %>% filter(construct=="PVQ_SD_tot" & prompt_type=="hybrid" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_ccr_po = df %>% filter(construct=="PVQ_PO_tot" & prompt_type=="hybrid" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_ccr_un = df %>% filter(construct=="PVQ_UN_tot" & prompt_type=="hybrid" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_ccr_ac = df %>% filter(construct=="PVQ_AC_tot" & prompt_type=="hybrid" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_ccr_se = df %>% filter(construct=="PVQ_SE_tot" & prompt_type=="hybrid" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_ccr_st = df %>% filter(construct=="PVQ_ST_tot" & prompt_type=="hybrid" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_ccr_co = df %>% filter(construct=="PVQ_CO_tot" & prompt_type=="hybrid" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_ccr_tr = df %>% filter(construct=="PVQ_TR_tot" & prompt_type=="hybrid" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_ccr_he = df %>% filter(construct=="PVQ_HE_tot" & prompt_type=="hybrid" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_ccr_be = df %>% filter(construct=="PVQ_BE_tot" & prompt_type=="hybrid" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")

gpt_ccr_cons_lm <- lm(response ~ item_1 + item_2, df_ccr_cons)
gpt_ccr_indi_lm <- lm(response ~ item_1 + item_2 + item_3 + item_4 + item_5 + item_6, df_ccr_indi)
gpt_ccr_reli_lm <- lm(response ~ item_1 + item_2 + item_3 + item_4 + item_5,          df_ccr_reli)
gpt_ccr_coll_lm <- lm(response ~ item_1 + item_2 + item_3 + item_4 + item_5 + item_6, df_ccr_coll)
gpt_ccr_care_lm <- lm(response ~ item_1 + item_2 + item_3 + item_4 + item_5 + item_6, df_ccr_care)
gpt_ccr_equa_lm <- lm(response ~ item_1 + item_2 + item_3 + item_4 + item_5 + item_6, df_ccr_equa)
gpt_ccr_prop_lm <- lm(response ~ item_1 + item_2 + item_3 + item_4 + item_5 + item_6, df_ccr_prop)
gpt_ccr_loya_lm <- lm(response ~ item_1 + item_2 + item_3 + item_4 + item_5 + item_6, df_ccr_loya)
gpt_ccr_auth_lm <- lm(response ~ item_1 + item_2 + item_3 + item_4 + item_5 + item_6, df_ccr_auth)
gpt_ccr_puri_lm <- lm(response ~ item_1 + item_2 + item_3 + item_4 + item_5 + item_6, df_ccr_puri)

gpt_ccr_nfc_lm <- lm(response ~ item_1 + item_2 + item_3 + item_4 + item_5 + item_6, df_ccr_nfc)
gpt_ccr_tigh_lm <- lm(response ~ item_1 + item_2 + item_3 + item_4 + item_5 + item_6, df_ccr_tigh)

gpt_ccr_sd_lm <- lm(response ~ item_1 + item_2, df_ccr_sd)
gpt_ccr_po_lm <- lm(response ~ item_1 + item_2, df_ccr_po)
gpt_ccr_un_lm <- lm(response ~ item_1 + item_2 + item_3, df_ccr_un)
gpt_ccr_ac_lm <- lm(response ~ item_1 + item_2, df_ccr_ac)
gpt_ccr_se_lm <- lm(response ~ item_1 + item_2, df_ccr_se)
gpt_ccr_st_lm <- lm(response ~ item_1 + item_2, df_ccr_st)
gpt_ccr_co_lm <- lm(response ~ item_1 + item_2, df_ccr_co)
gpt_ccr_tr_lm <- lm(response ~ item_1 + item_2, df_ccr_tr)
gpt_ccr_he_lm <- lm(response ~ item_1 + item_2, df_ccr_he)
gpt_ccr_be_lm <- lm(response ~ item_1 + item_2, df_ccr_be)
```


### GPT item-level scores (CCR style prompts) -- Everyday essays
```{r}
#model summaries
gpt_ccr_cons_summary = summary(gpt_ccr_cons_lm)
gpt_ccr_indi_summary = summary(gpt_ccr_indi_lm)
gpt_ccr_reli_summary = summary(gpt_ccr_reli_lm)
gpt_ccr_coll_summary = summary(gpt_ccr_coll_lm)
gpt_ccr_care_summary = summary(gpt_ccr_care_lm)
gpt_ccr_equa_summary = summary(gpt_ccr_equa_lm)
gpt_ccr_prop_summary = summary(gpt_ccr_prop_lm)
gpt_ccr_loya_summary = summary(gpt_ccr_loya_lm)
gpt_ccr_auth_summary = summary(gpt_ccr_auth_lm)
gpt_ccr_puri_summary = summary(gpt_ccr_puri_lm)

gpt_ccr_nfc_summary = summary(gpt_ccr_nfc_lm)
gpt_ccr_tigh_summary= summary(gpt_ccr_tigh_lm)
gpt_ccr_sd_summary= summary(gpt_ccr_sd_lm)
gpt_ccr_po_summary= summary(gpt_ccr_po_lm)
gpt_ccr_un_summary= summary(gpt_ccr_un_lm)
gpt_ccr_ac_summary= summary(gpt_ccr_ac_lm)
gpt_ccr_se_summary= summary(gpt_ccr_se_lm)
gpt_ccr_st_summary= summary(gpt_ccr_st_lm)
gpt_ccr_co_summary= summary(gpt_ccr_co_lm)
gpt_ccr_tr_summary= summary(gpt_ccr_tr_lm)
gpt_ccr_he_summary = summary(gpt_ccr_he_lm)
gpt_ccr_be_summary = summary(gpt_ccr_be_lm)

scores_gpt_ccr_behaviors = c(gpt_ccr_tigh_summary$r.squared,gpt_ccr_indi_summary$r.squared,
                          gpt_ccr_coll_summary$r.squared, gpt_ccr_nfc_summary$r.squared,
                          gpt_ccr_cons_summary$r.squared, gpt_ccr_reli_summary$r.squared,
           gpt_ccr_care_summary$r.squared, gpt_ccr_equa_summary$r.squared,
           gpt_ccr_prop_summary$r.squared, gpt_ccr_loya_summary$r.squared,
           gpt_ccr_auth_summary$r.squared, gpt_ccr_puri_summary$r.squared,
           gpt_ccr_sd_summary$r.squared, gpt_ccr_po_summary$r.squared,
           gpt_ccr_un_summary$r.squared, gpt_ccr_ac_summary$r.squared,
           gpt_ccr_se_summary$r.squared, gpt_ccr_st_summary$r.squared,
           gpt_ccr_co_summary$r.squared, gpt_ccr_tr_summary$r.squared,
           gpt_ccr_he_summary$r.squared, gpt_ccr_be_summary$r.squared)

names(scores_gpt_ccr_behaviors) <- colnames(df_scores_all)[3:length(colnames(df_scores_all))]

df_scores_gpt_ccr_behaviors <- as.data.frame(t(data.frame(scores_gpt_ccr_behaviors)))
df_scores_gpt_ccr_behaviors = cbind(source = "behaviors", df_scores_gpt_ccr_behaviors)
df_scores_gpt_ccr_behaviors = cbind(model = "gpt_ccr", df_scores_gpt_ccr_behaviors)
```


### GPT Construct-level models (general prompts) -- Values Essays
```{r}
# format data sets from long to wide for each construct separately
df_tot_cons = df %>% filter(construct=="conservatism_tot" & prompt_type=="general" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_tot_indi = df %>% filter(construct=="Individualism_tot" & prompt_type=="general" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_tot_reli = df %>% filter(construct=="Religiosity_tot" & prompt_type=="general" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_tot_coll = df %>% filter(construct=="Collectivism_tot" & prompt_type=="general" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_tot_care = df %>% filter(construct=="CARE_tot" & prompt_type=="general" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_tot_equa = df %>% filter(construct=="EQUALITY_tot" & prompt_type=="general" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_tot_prop = df %>% filter(construct=="PROPORTIONALITY_tot" & prompt_type=="general" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_tot_loya = df %>% filter(construct=="LOYALTY_tot" & prompt_type=="general" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_tot_auth = df %>% filter(construct=="AUTHORITY_tot" & prompt_type=="general" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_tot_puri = df %>% filter(construct=="PURITY_tot" & prompt_type=="general" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_tot_nfc = df %>% filter(construct=="NFC_tot" & prompt_type=="general" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_tot_tigh = df %>% filter(construct=="Tightness" & prompt_type=="general" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_tot_sd = df %>% filter(construct=="PVQ_SD_tot" & prompt_type=="general" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_tot_po = df %>% filter(construct=="PVQ_PO_tot" & prompt_type=="general" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_tot_un = df %>% filter(construct=="PVQ_UN_tot" & prompt_type=="general" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_tot_ac = df %>% filter(construct=="PVQ_AC_tot" & prompt_type=="general" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_tot_se = df %>% filter(construct=="PVQ_SE_tot" & prompt_type=="general" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_tot_st = df %>% filter(construct=="PVQ_ST_tot" & prompt_type=="general" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_tot_co = df %>% filter(construct=="PVQ_CO_tot" & prompt_type=="general" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_tot_tr = df %>% filter(construct=="PVQ_TR_tot" & prompt_type=="general" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_tot_he = df %>% filter(construct=="PVQ_HE_tot" & prompt_type=="general" & source=="values") %>% spread(key = "item", value = "prediction_clean")
df_tot_be = df %>% filter(construct=="PVQ_BE_tot" & prompt_type=="general" & source=="values") %>% spread(key = "item", value = "prediction_clean")

gpt_tot_cons_lm <- lm(response ~ total, df_tot_cons)
gpt_tot_indi_lm <- lm(response ~ total, df_tot_indi)
gpt_tot_reli_lm <- lm(response ~ total, df_tot_reli)
gpt_tot_coll_lm <- lm(response ~ total, df_tot_coll)
gpt_tot_care_lm <- lm(response ~ total, df_tot_care)
gpt_tot_equa_lm <- lm(response ~ total, df_tot_equa)
gpt_tot_prop_lm <- lm(response ~ total, df_tot_prop)
gpt_tot_loya_lm <- lm(response ~ total, df_tot_loya)
gpt_tot_auth_lm <- lm(response ~ total, df_tot_auth)
gpt_tot_puri_lm <- lm(response ~ total, df_tot_puri)

gpt_tot_nfc_lm <- lm(response ~ total, df_tot_nfc)
gpt_tot_tigh_lm <- lm(response ~ total, df_tot_tigh)

gpt_tot_sd_lm <- lm(response ~ total, df_tot_sd)
gpt_tot_po_lm <- lm(response ~ total, df_tot_po)
gpt_tot_un_lm <- lm(response ~ total, df_tot_un)
gpt_tot_ac_lm <- lm(response ~ total, df_tot_ac)
gpt_tot_se_lm <- lm(response ~ total, df_tot_se)
gpt_tot_st_lm <- lm(response ~ total, df_tot_st)
gpt_tot_co_lm <- lm(response ~ total, df_tot_co)
gpt_tot_tr_lm <- lm(response ~ total, df_tot_tr)
gpt_tot_he_lm <- lm(response ~ total, df_tot_he)
gpt_tot_be_lm <- lm(response ~ total, df_tot_be)
```


### GPT construct-level scores (general prompts) -- Values Essays
```{r}
#model summaries
gpt_tot_cons_summary = summary(gpt_tot_cons_lm)
gpt_tot_indi_summary = summary(gpt_tot_indi_lm)
gpt_tot_reli_summary = summary(gpt_tot_reli_lm)
gpt_tot_coll_summary = summary(gpt_tot_coll_lm)
gpt_tot_care_summary = summary(gpt_tot_care_lm)
gpt_tot_equa_summary = summary(gpt_tot_equa_lm)
gpt_tot_prop_summary = summary(gpt_tot_prop_lm)
gpt_tot_loya_summary = summary(gpt_tot_loya_lm)
gpt_tot_auth_summary = summary(gpt_tot_auth_lm)
gpt_tot_puri_summary = summary(gpt_tot_puri_lm)

gpt_tot_nfc_summary = summary(gpt_tot_nfc_lm)
gpt_tot_tigh_summary= summary(gpt_tot_tigh_lm)
gpt_tot_sd_summary= summary(gpt_tot_sd_lm)
gpt_tot_po_summary= summary(gpt_tot_po_lm)
gpt_tot_un_summary= summary(gpt_tot_un_lm)
gpt_tot_ac_summary= summary(gpt_tot_ac_lm)
gpt_tot_se_summary= summary(gpt_tot_se_lm)
gpt_tot_st_summary= summary(gpt_tot_st_lm)
gpt_tot_co_summary= summary(gpt_tot_co_lm)
gpt_tot_tr_summary= summary(gpt_tot_tr_lm)
gpt_tot_he_summary = summary(gpt_tot_he_lm)
gpt_tot_be_summary = summary(gpt_tot_be_lm)

scores_gpt_tot_values = c(gpt_tot_tigh_summary$r.squared,gpt_tot_indi_summary$r.squared,
                          gpt_tot_coll_summary$r.squared, gpt_tot_nfc_summary$r.squared,
                          gpt_tot_cons_summary$r.squared, gpt_tot_reli_summary$r.squared,
           gpt_tot_care_summary$r.squared, gpt_tot_equa_summary$r.squared,
           gpt_tot_prop_summary$r.squared, gpt_tot_loya_summary$r.squared,
           gpt_tot_auth_summary$r.squared, gpt_tot_puri_summary$r.squared,
           gpt_tot_sd_summary$r.squared, gpt_tot_po_summary$r.squared,
           gpt_tot_un_summary$r.squared, gpt_tot_ac_summary$r.squared,
           gpt_tot_se_summary$r.squared, gpt_tot_st_summary$r.squared,
           gpt_tot_co_summary$r.squared, gpt_tot_tr_summary$r.squared,
           gpt_tot_he_summary$r.squared, gpt_tot_be_summary$r.squared)

names(scores_gpt_tot_values) <- colnames(df_scores_all)[3:length(colnames(df_scores_all))]

df_scores_gpt_tot_values <- as.data.frame(t(data.frame(scores_gpt_tot_values)))
df_scores_gpt_tot_values <- cbind(source = "values", df_scores_gpt_tot_values)
df_scores_gpt_tot_values <- cbind(model = "gpt", df_scores_gpt_tot_values)
```

### GPT construct-level models -- Everyday Essays
```{r}
# format data sets from long to wide for each construct separately
df_tot_cons = df %>% filter(construct=="conservatism_tot" & prompt_type=="general" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_tot_indi = df %>% filter(construct=="Individualism_tot" & prompt_type=="general" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_tot_reli = df %>% filter(construct=="Religiosity_tot" & prompt_type=="general" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_tot_coll = df %>% filter(construct=="Collectivism_tot" & prompt_type=="general" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_tot_care = df %>% filter(construct=="CARE_tot" & prompt_type=="general" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_tot_equa = df %>% filter(construct=="EQUALITY_tot" & prompt_type=="general" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_tot_prop = df %>% filter(construct=="PROPORTIONALITY_tot" & prompt_type=="general" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_tot_loya = df %>% filter(construct=="LOYALTY_tot" & prompt_type=="general" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_tot_auth = df %>% filter(construct=="AUTHORITY_tot" & prompt_type=="general" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_tot_puri = df %>% filter(construct=="PURITY_tot" & prompt_type=="general" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_tot_nfc = df %>% filter(construct=="NFC_tot" & prompt_type=="general" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_tot_tigh = df %>% filter(construct=="Tightness" & prompt_type=="general" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_tot_sd = df %>% filter(construct=="PVQ_SD_tot" & prompt_type=="general" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_tot_po = df %>% filter(construct=="PVQ_PO_tot" & prompt_type=="general" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_tot_un = df %>% filter(construct=="PVQ_UN_tot" & prompt_type=="general" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_tot_ac = df %>% filter(construct=="PVQ_AC_tot" & prompt_type=="general" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_tot_se = df %>% filter(construct=="PVQ_SE_tot" & prompt_type=="general" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_tot_st = df %>% filter(construct=="PVQ_ST_tot" & prompt_type=="general" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_tot_co = df %>% filter(construct=="PVQ_CO_tot" & prompt_type=="general" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_tot_tr = df %>% filter(construct=="PVQ_TR_tot" & prompt_type=="general" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_tot_he = df %>% filter(construct=="PVQ_HE_tot" & prompt_type=="general" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")
df_tot_be = df %>% filter(construct=="PVQ_BE_tot" & prompt_type=="general" & source=="behaviors") %>% spread(key = "item", value = "prediction_clean")

gpt_tot_cons_lm <- lm(response ~ total, df_tot_cons)
gpt_tot_indi_lm <- lm(response ~ total, df_tot_indi)
gpt_tot_reli_lm <- lm(response ~ total, df_tot_reli)
gpt_tot_coll_lm <- lm(response ~ total, df_tot_coll)
gpt_tot_care_lm <- lm(response ~ total, df_tot_care)
gpt_tot_equa_lm <- lm(response ~ total, df_tot_equa)
gpt_tot_prop_lm <- lm(response ~ total, df_tot_prop)
gpt_tot_loya_lm <- lm(response ~ total, df_tot_loya)
gpt_tot_auth_lm <- lm(response ~ total, df_tot_auth)
gpt_tot_puri_lm <- lm(response ~ total, df_tot_puri)

gpt_tot_nfc_lm <- lm(response ~ total, df_tot_nfc)
gpt_tot_tigh_lm <- lm(response ~ total, df_tot_tigh)

gpt_tot_sd_lm <- lm(response ~ total, df_tot_sd)
gpt_tot_po_lm <- lm(response ~ total, df_tot_po)
gpt_tot_un_lm <- lm(response ~ total, df_tot_un)
gpt_tot_ac_lm <- lm(response ~ total, df_tot_ac)
gpt_tot_se_lm <- lm(response ~ total, df_tot_se)
gpt_tot_st_lm <- lm(response ~ total, df_tot_st)
gpt_tot_co_lm <- lm(response ~ total, df_tot_co)
gpt_tot_tr_lm <- lm(response ~ total, df_tot_tr)
gpt_tot_he_lm <- lm(response ~ total, df_tot_he)
gpt_tot_be_lm <- lm(response ~ total, df_tot_be)
```


### GPT construct-level scores (general prompts) -- Everyday Essays
```{r}
#model summaries
gpt_tot_cons_summary = summary(gpt_tot_cons_lm)
gpt_tot_indi_summary = summary(gpt_tot_indi_lm)
gpt_tot_reli_summary = summary(gpt_tot_reli_lm)
gpt_tot_coll_summary = summary(gpt_tot_coll_lm)
gpt_tot_care_summary = summary(gpt_tot_care_lm)
gpt_tot_equa_summary = summary(gpt_tot_equa_lm)
gpt_tot_prop_summary = summary(gpt_tot_prop_lm)
gpt_tot_loya_summary = summary(gpt_tot_loya_lm)
gpt_tot_auth_summary = summary(gpt_tot_auth_lm)
gpt_tot_puri_summary = summary(gpt_tot_puri_lm)

gpt_tot_nfc_summary = summary(gpt_tot_nfc_lm)
gpt_tot_tigh_summary= summary(gpt_tot_tigh_lm)
gpt_tot_sd_summary= summary(gpt_tot_sd_lm)
gpt_tot_po_summary= summary(gpt_tot_po_lm)
gpt_tot_un_summary= summary(gpt_tot_un_lm)
gpt_tot_ac_summary= summary(gpt_tot_ac_lm)
gpt_tot_se_summary= summary(gpt_tot_se_lm)
gpt_tot_st_summary= summary(gpt_tot_st_lm)
gpt_tot_co_summary= summary(gpt_tot_co_lm)
gpt_tot_tr_summary= summary(gpt_tot_tr_lm)
gpt_tot_he_summary = summary(gpt_tot_he_lm)
gpt_tot_be_summary = summary(gpt_tot_be_lm)

scores_gpt_tot_behaviors = c(gpt_tot_tigh_summary$r.squared,gpt_tot_indi_summary$r.squared,
                          gpt_tot_coll_summary$r.squared, gpt_tot_nfc_summary$r.squared,
                          gpt_tot_cons_summary$r.squared, gpt_tot_reli_summary$r.squared,
           gpt_tot_care_summary$r.squared, gpt_tot_equa_summary$r.squared,
           gpt_tot_prop_summary$r.squared, gpt_tot_loya_summary$r.squared,
           gpt_tot_auth_summary$r.squared, gpt_tot_puri_summary$r.squared,
           gpt_tot_sd_summary$r.squared, gpt_tot_po_summary$r.squared,
           gpt_tot_un_summary$r.squared, gpt_tot_ac_summary$r.squared,
           gpt_tot_se_summary$r.squared, gpt_tot_st_summary$r.squared,
           gpt_tot_co_summary$r.squared, gpt_tot_tr_summary$r.squared,
           gpt_tot_he_summary$r.squared, gpt_tot_be_summary$r.squared)

names(scores_gpt_tot_behaviors) <- colnames(df_scores_all)[3:length(colnames(df_scores_all))]

df_scores_gpt_tot_behaviors <- as.data.frame(t(data.frame(scores_gpt_tot_behaviors)))
df_scores_gpt_tot_behaviors = cbind(source = "behaviors", df_scores_gpt_tot_behaviors)
df_scores_gpt_tot_behaviors = cbind(model = "gpt", df_scores_gpt_tot_behaviors)
```


## Combine all results
```{r}
# append all scores into a single data frame
# only keep models and constructs that will be compared
df_scores_final <- bind_rows(df_scores_all, df_scores_gpt_ccr_behaviors, df_scores_gpt_ccr_values, 
          df_scores_gpt_tot_values, df_scores_gpt_tot_behaviors)
df_scores_final$model <- factor(df_scores_final$model, levels = c('ccr', "gpt", "gpt_ccr")) 
df_scores_final <- df_scores_final %>% drop_na(model) %>% select_if(~ !any(is.na(.)))
row.names(df_scores_final) <- 1:nrow(df_scores_final)
colnames(df_scores_final) <- c("source", "model", "Tightness",	"Individualism",	"Collectivism",	"Need For Cognition",	"Conservatism",	"Religiosity",	"Care",	"Equality",	"Proportionality",	"Loyalty",	"Authority",	"Purity",	"Self-Direction",	"Power",	"Universalism",	"Achievement",	"Security",	"Stimulation",	"Conformity",	"Tradition",	"Hedonism",	"Benevolence")

# split into 2 source texts
df_scores_final_value <- df_scores_final %>% filter(source == "values") %>% gather(key = "construct", value = "r2", -c(source, model))
df_scores_final_value[df_scores_final_value$model!="ccr", "r2"] = df_scores_final_value[df_scores_final_value$model!="ccr", "r2"]*100 #transform numerical to percentages
df_scores_final_behav <- df_scores_final %>% filter(source == "behaviors") %>% gather(key = "construct", value = "r2", -c(source, model))
df_scores_final_behav[df_scores_final_behav$model!="ccr", "r2"] = df_scores_final_behav[df_scores_final_behav$model!="ccr", "r2"] * 100 #transform numerical to percentages
```

## Statistical Tests
### Dunnett's Test (gpt & gpt_ccr vs CCR)
```{r}
f = as.formula("r2 ~ model")
print(DunnettTest(f, data = df_scores_final_value, control = "ccr")) # test for performance differences when using value essays
print(DunnettTest(f, data = df_scores_final_behav, control = "ccr")) # test for performance differences when using everyday essays
```

```{r}
# Behaviors
#vs gpt
t.test(df_scores_final_behav[df_scores_final_behav$model=="ccr", "r2"], df_scores_final_behav[df_scores_final_behav$model=="gpt", "r2"], alternative = "two.sided")

#vs gpt_ccr
t.test(df_scores_final_behav[df_scores_final_behav$model=="ccr", "r2"], df_scores_final_behav[df_scores_final_behav$model=="gpt_ccr", "r2"], alternative = "two.sided")
```


### Correlation of model performances
```{r}
# Values
#vs gpt
cor.test(df_scores_final_value[df_scores_final_value$model=="ccr", "r2"], df_scores_final_value[df_scores_final_value$model=="gpt", "r2"], alternative = "two.sided")

#vs gpt_ccr
cor.test(df_scores_final_value[df_scores_final_value$model=="ccr", "r2"], df_scores_final_value[df_scores_final_value$model=="gpt_ccr", "r2"], alternative = "two.sided")
```



```{r}
# Behaviors
#vs gpt
cor.test(df_scores_final_behav[df_scores_final_behav$model=="ccr", "r2"], df_scores_final_behav[df_scores_final_behav$model=="gpt", "r2"], alternative = "two.sided")

#vs gpt_ccr
cor.test(df_scores_final_behav[df_scores_final_behav$model=="ccr", "r2"], df_scores_final_behav[df_scores_final_behav$model=="gpt_ccr", "r2"], alternative = "two.sided")
```


### Plots
#### Values essays
```{r}
###### Means and CI
mean_ccr_values <- t.test(df_scores_final_value[df_scores_final_value$model=="ccr", "r2"])[5]$estimate
ci_ccr_values <- t.test(df_scores_final_value[df_scores_final_value$model=="ccr", "r2"])$conf.int

mean_gpt_values <- t.test(df_scores_final_value[df_scores_final_value$model=="gpt", "r2"])[5]$estimate
ci_gpt_values <- t.test(df_scores_final_value[df_scores_final_value$model=="gpt", "r2"])$conf.int

mean_gpt_ccr_values <- t.test(df_scores_final_value[df_scores_final_value$model=="gpt_ccr", "r2"])[5]$estimate
ci_gpt_ccr_values <- t.test(df_scores_final_value[df_scores_final_value$model=="gpt_ccr", "r2"])$conf.int

########## Plots
v_plot <- ggplot(df_scores_final_value, aes(x=construct,y=r2, color=model)) + geom_point() + theme_bw() + scale_color_discrete(name="Method", breaks=c("ccr", "gpt", "gpt_ccr"),
                         labels=c("CCR", "GPT (construct-level)", "GPT (item-level)")) +
  xlab("") + ylab("Variance explained (%)") + geom_hline(aes(yintercept = mean_ccr_values),color="red", linetype = "dashed") + geom_hline(aes(yintercept = mean_gpt_values),color="forestgreen", linetype = "dashed") + geom_hline(aes(yintercept = mean_gpt_ccr_values),color="steelblue3", linetype = "dashed") + geom_rect(aes(ymin=ci_ccr_values[1], ymax=ci_ccr_values[2],xmin=-Inf,xmax=Inf), fill='firebrick', color=NA, alpha= 0.005) + geom_rect(aes(ymin=ci_gpt_values[1], ymax=ci_gpt_values[2],xmin=-Inf,xmax=Inf), fill='forestgreen', color=NA, alpha= 0.005) + geom_rect(aes(ymin=ci_gpt_ccr_values[1], ymax=ci_gpt_ccr_values[2],xmin=-Inf,xmax=Inf), fill='steelblue3', color=NA, alpha= 0.005) + coord_flip()

v_plot

ggsave("../results/plots/r2_values.png", v_plot, height = 4, width=6, dpi = 150, device = "png")
```


#### Everyday essays
```{r}
### means and CI
mean_ccr_behaviors <- t.test(df_scores_final_behav[df_scores_final_behav$model=="ccr", "r2"])[5]$estimate
ci_ccr_behaviors <- t.test(df_scores_final_behav[df_scores_final_behav$model=="ccr", "r2"])$conf.int

mean_gpt_behaviors <- t.test(df_scores_final_behav[df_scores_final_behav$model=="gpt", "r2"])[5]$estimate
ci_gpt_behaviors <- t.test(df_scores_final_behav[df_scores_final_behav$model=="gpt", "r2"])$conf.int

mean_gpt_ccr_behaviors <- t.test(df_scores_final_behav[df_scores_final_behav$model=="gpt_ccr", "r2"])[5]$estimate
ci_gpt_ccr_behaviors <- t.test(df_scores_final_behav[df_scores_final_behav$model=="gpt_ccr", "r2"])$conf.int

###### Plots
v_plot <- ggplot(df_scores_final_value, aes(x=construct,y=r2, color=model)) + geom_point() + theme_bw() + scale_color_discrete(name="Method", breaks=c("ccr", "gpt", "gpt_ccr"),
                         labels=c("CCR", "GPT (construct-level)", "GPT (item-level)")) +
  xlab("") + ylab("Variance explained (%)") + geom_hline(aes(yintercept = mean_ccr_behaviors),color="red", linetype = "dashed") + geom_hline(aes(yintercept = mean_gpt_behaviors),color="forestgreen", linetype = "dashed") + geom_hline(aes(yintercept = mean_gpt_ccr_behaviors),color="steelblue3", linetype = "dashed") + geom_rect(aes(ymin=ci_ccr_behaviors[1], ymax=ci_ccr_behaviors[2],xmin=-Inf,xmax=Inf), fill='firebrick', color=NA, alpha= 0.005) + geom_rect(aes(ymin=ci_gpt_behaviors[1], ymax=ci_gpt_behaviors[2],xmin=-Inf,xmax=Inf), fill='forestgreen', color=NA, alpha= 0.005) + geom_rect(aes(ymin=ci_gpt_ccr_behaviors[1], ymax=ci_gpt_ccr_behaviors[2],xmin=-Inf,xmax=Inf), fill='steelblue3', color=NA, alpha= 0.005) + coord_flip()

v_plot

ggsave("../results/plots/r2_behaviors.png", v_plot, height = 4, width=6, dpi = 150, device = "png")
```






